Demystifying the Combination of Dynamic Slicing and \\ Spectrum-based Fault Localization

### 2019-02-21 paper/ijcai/paper.tex
polishing and shortening abstract

\begin{abstract}
Several approaches have been proposed in the literature to improve debugging
costs through automated software fault diagnosis.  Dynamic Slicing (\ds{}) and
Spectrum-based Fault Localization (\sfl{}) are very popular fault diagnosis
techniques and normally seen as complementary.  This paper reports the outcome
of a study using real-world applications with the goal of demystifying the
impact of combining \ds{} with \sfl{}.  We suspect that several highly
suspicious components---often involved in failing, but seldom in passing
executions---may be unrelated to the bug. With the aforementioned combination,
such components could be identified and their suspiciousness reduced.  This
study also discusses the impact of the dynamic slicing key limitation---the risk
of missing faulty statements. Our results show that, in practice, \ds{} rarely
misses faulty statements (23 misses in 260 cases) and that the
\ds{}-\sfl{} combination, coined as Tandem-SL, improves the diagnostic accuracy
in 51\% of the faults. To sum, we found that, despite tacit opinions of the
research community about the usefulness of \ds{} in automated debugging, we
found the combination practical and effective, and encourage new \sfl{}
techniques to be evaluated against that optimization.
\end{abstract}

@@

@@

In \textbf{RQ1}, our concern is to evaluate how often \ds{} misses faulty
statements,  since it is one of the main issues of dynamic slicing techniques.
This is particularly important because when \ds{} missing a faulty statement
means that it will not be in the diagnostic report and therefore has a negative
impact in the fault localization accuracy. Table \ref{table:fsws}  presents the
number of faults where at least one of the faulty statements appears  in the
final reports of both techniques, \sfl{}$^{k}$ and \combpar{k}. For each fault,
we  only search for faulty statements in the top $5$ ($k=5$) and $10$ ($k=10$)
of the highest faulty  classes. \combpar{k} finds the faulty statements faster
than  \sfl{}$^{k}$. \Rui{Starting from here, I don't see the connection with
the rq... the rq has nothing to do with the combination. We need to somehow
motivate why we are discussing these numbers here.}
Using \combpar{10} we are able to find more $20$ faulty
statements than when only using \sfl{}$^{10}$. \combpar{10} only misses $11.8\%$
of the faulty statements whereas \sfl{}$^{10}$ misses $17.9\%$ of the faulty
statements. Thus, \combpar{10} misses less $5.2\%$ of the faults against
\sfl{}$^{10}$.

@@

In \textbf{RQ2}, we intend to evaluate the impact of combining \ds{} with \sfl{}
to improve fault localization. Table~\ref{table:st}, reports the average rank of all faulty
statements of the \dfj{} faults considered to the study after applying the both
techniques, \sfl{}$^{k}$ and \combpar{k} for $K=5$ and $k=10$. We observe that
$33$ of the $260$ \Rui{Ehmm... is this in sycn with previous section?}
faulty versions do not include the faulty statements in the slicer report after slicing.
Thus, we report both values in Table~\ref{table:st}. In bold, we present the
results of the $227$ faults that do not contain the cases where the faulty
statements where removed using \combpar{k}. Inside parentheses, we present the
rank results for all faults. The \combpar{k} combination yields an improvement
of $13.0$ on the rank mean of the dataset faulty statements when using $K=5$.
Instead, if $K=10$ is considered the proposed approach returns an improvement of
$11.1$ on the rank mean of faulty statements.
\Rui{APR doesn't belong here, maybe the last thing to discuss in this section,
but not here in the middle}
It is worth noting that Automated
Program Repair techniques may directly benefit from this study to improve their
results. Figure \ref{fig:diagnosis} reports the performance of the diagnosis
using \combpar{5} and \combpar{10} against \sfl{}$^{5}$ and \sfl{}$^{10}$,
respectively. Although this dataset has more than 50\% of fault of omissions,
our simple slicing approach was capable of improving the ranking of $97$ for
$k=5$ and $117$ for $K=117$ faults. Table \ref{table:st} presents the statistics
to determine if the observed results are statistically significant. Shapiro-Wilk
tests the null hypothesis that results are drawn from a normal distribution. The
test is perfomed for all techniques and its variants. With 99\% of confidence,
the results tell us that the distributions are not normal. Given that $C$ is not
normally distributed, we use the non-parametrical statistical hypothesis test,
Friedman. The null-hypothesis is that the ranking results of all techniques and
variants are the same. With 99\% of confidence, the results show that the
distributions are distinct. To understand if there exist a pair of
distributions that are equal \Rui{equal? isn't this test the effect size?}, we performed a Siegel post-hoc analysis. Figure
\ref{fig:performance} reports the results of Siegel analysis for all the
distributions. With 99\% of confidence, it is possible to see that in general
the distributions are very similar. \Rui{so??}

@@

\begin{figure}[h]
	\vspace{-1.5cm}
		\includegraphics[width=0.45\textwidth]{figures/heatmap_nemenyi_result.pdf}
		\caption{Siegel post-hoc analysis results}
		\label{fig:performance}
\end{figure}

>>>>

\begin{abstract}
Several approaches have been proposed in the literature to reduce
debugging costs through automated software fault diagnosis.  Dynamic
Slicing (\ds{}) and Spectrum-based Fault Localization (\sfl{}) are
popular fault diagnosis techniques and normally seen as complementary.
This paper reports on a comprehensive study\comments{--using
  \numFaults{} documented software faults from a credible dataset--}
to evaluate the effects of combining \ds{} with \sfl{}. We suspect
that several highly suspicious components---often involved in failing,
but seldom in passing test runs---may be unrelated to the bug. With
the aforementioned combination, such components could be located and
their suspiciousness reduced.  This study also discusses the practical
impact of the \ds{} key limitation---the risk of missing faulty
statements. Results indicate that \ds{} misses faulty statements in
only 9\%\comments{(23 misses)} of the 260 cases\Mar{we are using
  \numFaults{} in the paper. please, revise and use macros.} and that
the \ds{}-\sfl{} combination, coined as Tandem-SL, improves on average
the diagnostic accuracy by \Fix{Z} in 51\% of the cases. To sum, we
found that the \ds{}-\sfl{} combination was practical and effective
and encourage new \sfl{} techniques to be evaluated against that
optimization.
\end{abstract}

@@

\Mar{move this elsewhere...}
\Fix{
with the
goal of demystifying the impact of combining \ds{} with \sfl{}.

Despite tacit negative opinions of the research
community about the usefulness of \ds{} in automated debugging,}

@@

In \textbf{RQ1}, our concern is to evaluate how often \ds{} misses faulty
statements,  since it is one of the main issues of dynamic slicing techniques. This 
is particularly important because when \ds{} misses a faulty statement
means that it will not be in the diagnostic report and therefore has a negative
impact in the fault localization accuracy. Table~\ref{table:fsws}  presents the
number of faults where at least one of the faulty statements appears  in the
final reports of both techniques, \sfl{}$^{k}$ and \combpar{k}. For each fault,
we  only search for faulty statements in the top $5$ ($k=5$) and $10$ ($k=10$)
of the highest faulty  classes.

As observed in~\ref{table:fsws}, \combpar{k} 
finds the faulty statements faster than \sfl{}$^{k}$.

We observe that $33$ of the $260$ faulty versions do not include the 
faulty statements in the slicer report after slicing.

Using \combpar{10} we are able to find more $20$ faulty
statements than when only using \sfl{}$^{10}$. \combpar{10} only misses $11.8\%$
of the faulty statements whereas \sfl{}$^{10}$ misses $17.9\%$ of the faulty
statements. Thus, \combpar{10} misses less $5.2\%$ of the faults against
\sfl{}$^{10}$.

@@

In \textbf{RQ2}, we intend to evaluate the impact of combining \ds{} with \sfl{}
to improve fault localization. Table~\ref{table:st}, reports the average rank of all faulty
statements of the \dfj{} faults considered to the study after applying the both
techniques, \sfl{}$^{k}$ and \combpar{k} for $K=5$ and $k=10$. We observe that
$33$ of the $260$ 
faulty versions do not include the faulty statements in the slicer report after slicing.
Thus, we report both values in Table~\ref{table:st}. In bold, we present the
results of the $227$ faults that do not contain the cases where the faulty
statements where removed using \combpar{k}. Inside parentheses, we present the
rank results for all faults. The \combpar{k} combination yields an improvement
of $13.0$ on the rank mean of the dataset faulty statements when using $K=5$.
Instead, if $K=10$ is considered the proposed approach returns an improvement of
$11.1$ on the rank mean of faulty statements.
 Figure \ref{fig:diagnosis} reports the performance of the diagnosis
using \combpar{5} and \combpar{10} against \sfl{}$^{5}$ and \sfl{}$^{10}$,
respectively. Although this dataset has more than 50\% of fault of omissions,
our simple slicing approach was capable of improving the ranking of $97$ for
$k=5$ and $117$ for $K=117$ faults. Table \ref{table:st} presents the statistics
to determine if the observed results are statistically significant. Shapiro-Wilk
tests the null hypothesis that results are drawn from a normal distribution. The
test is perfomed for all techniques and its variants. With 99\% of confidence,
the results tell us that the distributions are not normal. Given that $C$ is not
normally distributed, we use the non-parametrical statistical hypothesis test,
Friedman. The null-hypothesis is that the ranking results of all techniques and
variants are the same. With 99\% of confidence, the results show that the
distributions are distinct. To understand if there is any relationship
between the distributions, 
we performed a Siegel post-hoc analysis. Figure
\ref{fig:performance} reports the results of Siegel analysis for all the
distributions. With 99\% of confidence, it is possible to see that in general
the distributions are very similar. \Rui{so??}

It is worth noting that Automated
Program Repair techniques may directly benefit from this study to improve their
results.

@@

\begin{figure}[h]
	\vspace{-1.2cm}
		\includegraphics[width=0.45\textwidth]{figures/heatmap_nemenyi_result.pdf}
		\caption{Siegel post-hoc analysis results}
		\label{fig:performance}
\end{figure}
